### 2016-11-09 thesis/intro/intro.tex
tmp commit

\gls{pomc} is a precursor protein that is cleaved to produce adrenocorticotropin (ACTH), $\alpha$-, $\beta$- and $\gamma$-\gls{msh}, and $\beta$-endorphin (citation Smith1988, endocr. rev.).
Perhaps the most important, or most relevant, in the context of obesity and satiety control is the $\alpha$-MSH.
$\alpha$-MSH is the main ligand that binds to the \gls{mc4r} expressed in the brain, and sends anorexogenic signals to the downstream neurons through this pathway \citep{Krude1998}.

@@

There are many hormones in your body that regulates various physiological aspects of your body.
Out of the many, four hormones have an important role in regulating the satiety of an individual: ghrelin, leptin, insulin, and \gls{pyy}.

Ghrelin is a hormone produced mainly in the stomach that has a role in meal initiation and food intake \citep{Kohno2003}.

Leptin, on the otherhand, is a hormone that has an opposite effect as ghrelin, where the hormone signals satiety and reduces food intake.

Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.

The last hormone is the \gls{pyy}, a peptide hormone released by the distal gastrointestinal tract that produces an anorexogenic signal.
\citep{Batterham2002}

>>>>

\gls{pomc} is a precursor protein that is cleaved to produce \gls{acth}, $\alpha$-, $\beta$- and $\gamma$-\gls{msh}, and $\beta$-endorphin (citation Smith1988, endocr. rev.).
Perhaps the most important, or most relevant, in the context of obesity and satiety control is the $\alpha$-MSH.
$\alpha$-MSH is the main ligand that binds to the \gls{mc4r} expressed in the brain, and sends anorexogenic signals to the downstream neurons through this pathway \citep{Krude1998}.

@@

There are many hormones in your body that regulates various physiological aspects of your body.
Out of the many, four hormones in particular have an important role in regulating the satiety of an individual: ghrelin, leptin, insulin, and \gls{pyy}.\\

\noindent
Ghrelin, originally identified as a peptide that stimulated the release of growth hormone from the pituitary, is a hormone produced mainly in the stomach that has a significant role in meal initiation and food intake, as well as energy homeostasis \citep{Kohno2003} (citation, nakazato2001 nature, kojima1999 nature).
Ghrelin is known to be a ligand for the \gls{ghsr} which is expressed abundantly on the \gls{npy}/\gls{agrp} neurons, and increases the Ca$^{2+}$ concentration in these neurons \citep{Kohno2003}.

Furthermore, (citation Seaone2003) showed that ghrelin increased the mRNA levels of both \gls{npy} and \gls{agrp} in these neurons and hence their protein expression, indicating the role of ghrelin as the orexogenic hormone that affects the overall outcome of the satiety signal.
\\

\noindent
Leptin, on the otherhand, is a hormone that has an opposite effect as ghrelin, where the hormone signals satiety and reduces food intake.
First identified by \citet{Zhang1994}, the dicovery of the leptin gene, followed by the discovery of leptin receptor gene by \citet{Tartaglia1995}, were probably the major breakthrough in the field of obesity research.
\\

\noindent
Insulin, perhaps the most well-known hormone for its role in glucose homeostasis, also has an important role in satiety and food intake regulation.
\\

\noindent
The last hormone is the \gls{pyy}, a peptide hormone released by the distal gastrointestinal tract that produces an anorexogenic signal.
\citep{Batterham2002}
